Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-08-24 paper/main.tex
[DATALAD] auto-saved changes

% av intro
First, we analyzed data from the movie that offered ecologically more valid
visual stimulation than a paradigm using blocks of pictures.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to a setting that was not
depicted before to cuts within a recurring setting (\texttt{vse\_new >
vpe\_old}) yielded three significant clusters (see Table~\ref{tab:res-av-group1},
Figure~\ref{fig:group-slices}, and Supplementary
Figure~\ref{fig:grp_ao_av_c1_surf} for results mapped onto reconstructed
cortical surface).
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises parts of the intracalcarine
and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
temporal fusiform gyrus, and the parahippocampal cortex (reported from posterior
to anterior) in both hemispheres.
% LOC
Two additional bilateral clusters are located in the superior lateral occipital
cortex.

% AD intro
Second, we analyzed data from the audio-description offering an exclusively
auditory stimulation.
% AD primary contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters
(see Table~\ref{tab:res-ao-group1}, Figure~\ref{fig:group-slices}, and
Supplementary Figure~\ref{fig:grp_ao_av_c1_surf} surface plots).
% overlap with ROI
Two bilateral clusters are located in the anterior part of the PPA group overlap
reported by \citet{sengupta2016extension}.
% in detail
Specifically, these clusters are located at the borders of the posterior
parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
gyrus.
% precuneus
Two additional bilateral clusters are apparent in the ventral precuneus
extending into the retrosplenial cortex.
% LOC
Finally, two bilateral clusters are located in the superior lateral occipital
cortex.

@@

    \caption{Mixed-effects group-level (N=14) clusters ($Z$>3.4, $p$<.05
      cluster-corrected) of activity correlated with the processing of spatial
      information are displayed on top of the MNI152 T1-weighted head template,
      with the acquisition field-of-view for the audio-description study
      highlighted.
      %
      The results of the audio-description's primary $t$-contrast (blue) that
      compares geometry-related nouns spoken by the narrator to non-spatial
      nouns (\texttt{geo, groom} > all non-spatial categories) are overlaid
      on the movie's primary $t$-contrast (red) that compares cuts to a
      setting depicted for the first time with cuts within a recurring setting
      (\texttt{vse\_new > vpe\_old}).
      %
      For comparison, the union of the individual PPA localization reported
      by \citet{sengupta2016extension} are indicated as a black outline.
    }

    \label{fig:group-slices}
\end{figure*}

>>>>

\todo[inline]{Since we did no analyses in surface space imo it makes more sense
    to explain the ``method'' to create the surface plots here in the
``Results''}

\todo[inline]{only Captions mention smoothing of union of PPAs; Volume FWHM was
2mm, Surface FWHM was 3mm}

\todo[inline]{Merge plots and adjust references here}

% av intro
First, we analyzed data from the movie that offered ecologically more valid
visual stimulation than a paradigm using blocks of pictures.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to a setting that was not
depicted before to cuts within a recurring setting (\texttt{vse\_new >
vpe\_old}) yielded three significant clusters (see
Table~\ref{tab:res-av-group1}).
% volume plots
Results are depicted as slices of brain volumes in Figure~\ref{fig:grp_ao_av_c1_volsurf} a).
% surface plots
The surface plots depicted in \ref{fig:grp_ao_av_c1_volsurf} b) were created by
reconstructing the cortical surface of the MNI152 template using
\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer} v7.1.1
\citep{dale1999cortical} and projecting the $Z$-maps onto the surface using
FreeSurfer's 'mri\_vol2surf' command.
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises parts of the intracalcarine
and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
temporal fusiform gyrus, and the parahippocampal cortex (reported from posterior
to anterior) in both hemispheres.
% LOC
Two additional bilateral clusters are located in the superior lateral occipital
cortex.

% AD intro
Second, we analyzed data from the audio-description offering an exclusively
auditory stimulation.
% AD primary contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters
(see Table~\ref{tab:res-ao-group1}, Figure~\ref{fig:grp_ao_av_c1_volsurf} a) as volume plots, and Figure~\ref{fig:grp_ao_av_c1_volsurf} b) as surface plots).
% overlap with ROI
Two bilateral clusters are located in the anterior part of the PPA group overlap
reported by \citet{sengupta2016extension}.
% in detail
Specifically, these clusters are located at the borders of the posterior
parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
gyrus.
% precuneus
Two additional bilateral clusters are apparent in the ventral precuneus
extending into the retrosplenial cortex.
% LOC
Finally, two bilateral clusters are located in the superior lateral occipital
cortex.

@@

    \caption{Mixed-effects group-level (N=14) clusters ($Z$>3.4, $p$<.05
      cluster-corrected) of activity correlated with the processing of spatial
      information are displayed on top of the MNI152 T1-weighted head template,
      with the acquisition field-of-view for the audio-description study
      highlighted.
      %
      The results of the audio-description's primary $t$-contrast (blue) that
      compares geometry-related nouns spoken by the narrator to non-spatial
      nouns (\texttt{geo, groom} > all non-spatial categories) are overlaid
      on the movie's primary $t$-contrast (red) that compares cuts to a
      setting depicted for the first time with cuts within a recurring setting
      (\texttt{vse\_new > vpe\_old}).
      %
      For comparison, the union of the individual PPA localization reported
      by \citet{sengupta2016extension} are indicated as a black outline.
    }
    \label{fig:group-slices}
\end{figure*}

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/grp_ao_av_c1_surf}

    \caption{Mixed-effects group-level (N=14) clusters ($Z$>3.4, $p$<.05
      cluster-corrected) of activity correlated with the processing of spatial
      information.
      a) Results are displayed on top of the MNI152 T1-weighted head template,
      with the acquisition field-of-view for the audio-description study
      highlighted.
      The results of the audio-description's primary $t$-contrast (blue) that
      compares geometry-related nouns spoken by the narrator to non-spatial
      nouns (\texttt{geo, groom} > all non-spatial categories) are overlaid
      on the movie's primary $t$-contrast (red) that compares cuts to a
      setting depicted for the first time with cuts within a recurring setting
      (\texttt{vse\_new > vpe\_old}).
      % PPA
      For comparison depicted as a black outline, the union of the
      individual PPA localization reported by \citet{sengupta2016extension}
      that was spatially smoothed applying a Gaussian kernel with full
      width at half maximum (FWHM) of \unit[2.0]{mm}
      % surface map
      b) The results are displayed as projections onto the reconstructed
      surface of the MNI152 T1-weighted brain template. After projection the
      union of individual PPA localizations was spatially smoothed by a
      Gaussian kernel with FWHM of \unit[3.0]{mm}.
    }
    \label{fig:grp_ao_av_c1_volsurf}
\end{figure*}

### 2021-08-24 paper/suppl.tex
[DATALAD] auto-saved changes

    \caption[Mixed-effects group-level (N=14) clusters ($Z$>3.4, $p$<.05
      cluster-corrected) of activity correlated with the processing of spatial
      information are projected onto the surface of the MNI152
      T1-weighted brain template.]
      %
      {The results of the audio-description's primary $t$-contrast (blue) that
      compares geometry-related nouns spoken by the narrator to non-spatial
      nouns (\texttt{geo, groom} > all non-spatial categories) are overlaid
      on the movie's primary $t$-contrast (red) that compares cuts to a
      setting depicted for the first time with cuts within a recurring setting
      (\texttt{vse\_new > vpe\_old}).
      %
      Black: outline of the union of individual PPA ROIs reported by
      \citet{sengupta2016extension}.
    }
    \label{fig:grp_ao_av_c1_surf}
\end{figure*}

@@

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/stability-slices}
    \caption[Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
        corrected) across all contrasts for both naturalistic stimuli.]
        {The audio-description's contrasts 1-8 (blue)
        are overlaid over the audio-visual movie's contrasts 1-5 (red;
        see Table~\ref{tab:contrasts}).
        Cluster are overlaid on top of the MNI152 T1-weighted head template
        with the acquisition field-of-view for the audio-description study
        highlighted.
        Black: outline of the union of individual PPA ROIs reported by
        \citet{sengupta2016extension}.
        }
    \label{fig:stability-slices}
\end{figure*}

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/grp_ao_av_stability_surf}
    \caption[Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
    corrected) across all contrasts for both naturalistic stimuli projected onto
the surface of the MNI152 T1-weighted brain template.]
    {The audio-description's contrasts 1-8 (blue)
        are overlaid over the audio-visual movie's contrasts 1-5 (red;
        \ref{tab:contrasts}).
        Black: outline of the union of individual PPA ROIs reported by
        \citet{sengupta2016extension}.
        }
    \label{fig:grp_ao_av_stability}
\end{figure*}

>>>>

    \caption[NAME]
    {Mixed-effects group-level (N=14) clusters ($Z$>3.4, $p$<.05
    cluster-corrected) of activity correlated with the processing of spatial
    information are projected onto the surface of the MNI152
    T1-weighted brain template.
    %
    The results of the audio-description's primary $t$-contrast (blue) that
    compares geometry-related nouns spoken by the narrator to non-spatial
    nouns (\texttt{geo, groom} > all non-spatial categories) are overlaid
    on the movie's primary $t$-contrast (red) that compares cuts to a
    setting depicted for the first time with cuts within a recurring setting
    (\texttt{vse\_new > vpe\_old}).
    %
    Black: outline of the union of individual PPA ROIs reported by
    \citet{sengupta2016extension}.
    }
    \label{fig:grp_ao_av_c1_surf}
\end{figure*}

@@

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/stability-slices}
    \caption[NAME]
    {Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
    corrected) across all contrasts for both naturalistic stimuli.
    The audio-description's contrasts 1-8 (blue)
    are overlaid over the audio-visual movie's contrasts 1-5 (red;
    see Table~\ref{tab:contrasts}).
    Cluster are overlaid on top of the MNI152 T1-weighted head template
    with the acquisition field-of-view for the audio-description study
    highlighted.
    Black: outline of the union of individual PPA ROIs reported by
        \citet{sengupta2016extension}.
    }
    \label{fig:stability-slices}
\end{figure*}

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/grp_ao_av_stability_surf}
    \caption[NAME]
    {Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
    corrected) across all contrasts for both naturalistic stimuli projected
    onto the surface of the MNI152 T1-weighted brain template.
    The audio-description's contrasts 1-8 (blue) are overlaid over the
    audio-visual movie's contrasts 1-5 (red; \ref{tab:contrasts}).
    Black: outline of the union of individual PPA ROIs reported by
    \citet{sengupta2016extension}.
    }
    \label{fig:grp_ao_av_stability}
\end{figure*}
